\subsubsection*{1.08 August 2009\label{1_08_August_2009}\index{1.08 August 2009}}
\begin{itemize}

\item 

Updated Clair::SynthCollection to generate synthetic documents based on (1 to 4)-grams.


\item 

Modified extract N-grams to optionally use CMU-LM.


\item 

Updated make\_synth\_collection.pl to fully utilize Clair::SyntheticCollection.


\item 

Fixed some Tokenizer issues.


\item 

Added summarize\_document.pl to the utilities.


\item 

Added summarize\_collection to the utilities.


\item 

Added learn.pl to the utilities.


\item 

Added classify.pl to the utilities.


\item 

Added extract\_features.pl


\item 

Added bigrams\_to\_rand\_doc.pl to the utilities.


\item 

Added make\_synth\_collection\_Menczer.pl to the utilities.


\item 

Added Clair::RandomWalk for random walk on graphs.


\item 

Added Clair::Harmonic for computing harmonic functions based on the Relaxation and Montecarlo methods


\item 

Added random\_walk.pl to the utilities.


\item 

Added harmonic.pl to the utilities.


\item 

Added directory\_to\_URL\_network.pl to the utilities.


\item 

Fixed a bug in the crawling code.


\item 

Added new tutorials.


\item 

Added new sections to the documentation.


\item 

Added Clair::Bio::GIN for gene interaction extraction.


\item 

Added an interface to Stanford parser in Clair::Utils::Parse


\item 

Added tag\_genes.pl to the utilities.


\item 

Added extract\_interactions.pl to the utilities.

\end{itemize}
\subsubsection*{1.07 June 2009\label{1_07_June_2009}\index{1.07 June 2009}}
\begin{itemize}

\item 

Added Clair::Network::Spectral for spectral partitioning using Fiedler Vector.


\item 

Made Clairlib independent of MEAD (MEAD is no more required for Clairlib).


\item 

Added Naive Bayes learning and classification.


\item 

Added tests for feature extraction, learning, classification.


\item 

Fixed a bug in Clair::Cluster::create\_lexical\_network().


\item 

Added sampling options to Clair::Cluster.


\item 

Added "No IDF" option and sampling capabilities to corpus\_to\_cos.pl utility.


\item 

Fixed documentation typos.


\item 

Added new tutorials to the documentation.


\item 

Fixed bug in Clair::Utils::CorpusDownload.


\item 

Added 'manual weights' option to make\_synth\_collection util.


\item 

Fixed bug in extract\_ngrams.

\end{itemize}
\subsubsection*{1.06 March 2009\label{1_06_March_2009}\index{1.06 March 2009}}
\begin{itemize}

\item 

Added Clair:Network:FordFulkerson


\item 

Added change\_perl\_path.pl  to the utilities.


\item 

Added new scripts to interface ACL Anthology Network.


\item 

Fixed a bug in split\_into\_sentences() of Clair::Document

\end{itemize}
\subsubsection*{1.05 July 2008\label{1_05_July_2008}\index{1.05 July 2008}}
\begin{itemize}

\item 

Fixed formatting bugs in CorpusDownload.pm


\item 

Added get\_predecessor\_matrix() function in Network.pm


\item 

Added get\_shortest\_path() function in Network.pm


\item 

Added  erase\_corpus.pl script


\item added erase\_isolated\_nodes.pl script
\item added --ignore-isolated-nodes in convert\_network.pl
\item added several options to print\_network\_stats.pl: a. --self-loop,
\item completed the descriptions of print\_network\_stats.pl: added the
note of --force into usage.
\item 

added sentence\_to\_docs.pl , lines\_to\_docs.pl under util folder

\end{itemize}
\subsubsection*{1.04B June 2008\label{1_04B_June_2008}\index{1.04B June 2008}}
\begin{itemize}

\item 

Added -no-duplicated-edges in convert\_network.pl


\item Added largest connected component in cos\_to\_stats.pl
\item Added full avergage shortest path in print\_network.pl
\item 

fixed divide by zero error in Network.pm, Betweeness.pm

\end{itemize}
\subsubsection*{1.04A April 2008\label{1_04A_April_2008}\index{1.04A April 2008}}
\begin{itemize}

\item 

Added Clair::Network::GirvanNewman algorithm to do hierarchical clustering


\item 

Added Clair::Network::KernighanLin algorithm to do graph partition

\end{itemize}
\subsubsection*{1.04 Feburary 2008\label{1_04_Feburary_2008}\index{1.04 Feburary 2008}}
\begin{itemize}

\item 

Added Clair::Network::AdamicAdar to compute the adamic/adar value for a given network corpus


\item 

Added Clair::ChisqIndependent to compute p-value and degree of freedom for Chi square

\end{itemize}
\subsubsection*{1.03 August 2007\label{1_03_August_2007}\index{1.03 August 2007}}
\begin{itemize}

\item Added functionality to perform community finding within weighted, undirected networks
\item Added util/chunk$\backslash$\_document.pl to break documents into smaller files by word number
\item Added option to retain punctuation for idf and tf queries
\item Added option to print out full lists of idf and tf values for a corpus
\item LexRank moved from Clair::Network to Clair::Network::Centrality::LexRank
\item LexRank use now follows the same use pattern as the other centrality modules\end{itemize}
\subsubsection*{1.02 July 2007\label{1_02_July_2007}\index{1.02 July 2007}}
\begin{itemize}

\item Distribution reorganized in standard format
\item Improved and expanded installation documentation (INSTALL)
\item Improved POD (inline) documentation
\item Additional examples
\item Updated PDF documentation\end{itemize}
\subsubsection*{1.01 May 2007\label{1_01_May_2007}\index{1.01 May 2007}}
\begin{itemize}

\item Added Phrase-based Retrieval and Fuzzy OR Queries
\item Extended Clairlib-ext with interfaces for the Cluster class and the Document class to the Weka machine learning toolkit
\item Added LSI functionality
\item Extended parsing of strings / files into Documents
\item Added perceptron learning and classification for documents\end{itemize}
\subsubsection*{1.0 RC1 April 2007\label{1_0_RC1_April_2007}\index{1.0 RC1 April 2007}}
\begin{itemize}

\item Moved all Clair modules beneath the Clair::* namespace, updated documentation
\item Improved Network Analysis, added Clustering Coefficients code
\item Added Network Generation and Statistics modules\end{itemize}
\subsubsection*{0.955 March 2007\label{0_955_March_2007}\index{0.955 March 2007}}
\begin{itemize}

\item Made it possible to distribute clairlib in two distributions, one containing core code and another containing code that may be dependent on other resources
\item Cleaned up unit tests\end{itemize}
\subsubsection*{0.953 February 2007\label{0_953_February_2007}\index{0.953 February 2007}}
\begin{itemize}

\item Fixed bugs in Clair::Cluster, Clair::Document involving stemming
\item Cleaned up t/ and test/ directories
\item Created util/ directory
\item Added scripts to util/ directory to:\begin{itemize}

\item Run a Google query and save the returned URLs to a file
\item Download files from a URL and build a corpus
\item Segment a document into sentences and build a corpus of the sentences
\item Take all documents in a directory and create a corpus
\item Index the corpus (compute TF*IDF, etc.)
\item Compute cosine similarity measures between all documents in a corpus
\item Generate networks corresponding to various cosine thresholds
\item Print network statistics about a network file
\item Generate plots of degree distribution and cosine transitions\end{itemize}

\item New methods in Clair::Network:\begin{verbatim}
    print_network_info
    get_network_info_as_string
    get_cumulative_distribution
    cumulative_power_law_exponent
    find_components
    newman_clustering_coefficient
    linear_regression
\end{verbatim}
\end{itemize}
